Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-04 main.tex
Updates from Overleaf

Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves with a log-rank test, and univariate Cox regression to screen prognostic factors.
The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).

@@

They validated their candidate genes by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}

@@

%%% ***
In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
Our approach describes an in-house workflow implemented in the R script, which runs on the Rstudio server.
Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
The independent HNSCC dataset (GSE65858) was used to validate this strategy.
The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.

>>>>

Xu and his colleagues\cite{Xu2021a} also identified their biomarkers by analysis of differentially-expressed genes (DEGs).
The gene expression was used to select the preliminary biomarkers.
The significant impact on patients' overall survival was evaluated by Kaplan–Meier survival curves with a log-rank test (\textit{P} value $< 0.01$), and univariate Cox regression.

@@

They validated the candidate genes by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}

@@

%%% ***
In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
Our approach describes an in-house workflow implemented in the R script, which runs on the Rstudio server.
Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
The independent HNSCC dataset (GSE65858) was used to validate this strategy.
The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate by gene-expression based survival analysis.
